---
abstract: |
  *This is the abstract. All chapters, excluding Preface, Introduction, and 
  Conclusions, shall have an abstract, summarizing the Chapter contents. 
  Abstract uses valid Markdown, but it shall be a single paragraph, without any 
  link or reference. The whole abstract must be in Italic.*
---

```{r setup}
#| include: false
library(ggplot2)
```

# Problem Definition {#sec-problem-definition}

## Subject Matter

### Equations

Equations can be written in LaTeX format. For example, the equation of a line is $y = mx + b$. The equation of a circle is $x^2 + y^2 = r^2$. Those are **inline equations**. Longer equations, that can be optionally numbered, are given as: 

$$
\begin{aligned}
y &= \beta_0 + \beta_1 x + \epsilon \\
\epsilon &\sim N(0, \sigma^2)
\end{aligned}
$${#eq-linear-model}

Equations can be referenced as in @eq-linear-model.


### Figures {#sec-figures}

::: column-margin
This is a side note. Use the `column-margin` class to create side notes. See also the [Quarto documentation](https://quarto.org/docs/authoring/figures.html).
:::

{{< lipsum 2 >}}

**Figures can be also created on the side margin, by using the `column: margin` chunk option in the R chunk. See the result in @fig-mtcars.**

```{r}
#| label: fig-mtcars
#| echo: false
#| column: margin
#| fig-cap: MPG vs horsepower, colored by transmission.
mtcars2 <- mtcars
mtcars2$am <- factor(
  mtcars$am, labels = c('automatic', 'manual')
)
ggplot(mtcars2, aes(hp, mpg, color = am)) +
  geom_point() +
  geom_smooth(formula = y ~ x, method = "loess") +
  theme(legend.position = 'bottom')
```

{{< lipsum 3 >}}

Images are probably better added as figures, as in @fig-placeholder. When needed, photographs can be set to take the full page width, as in @fig-placeholder2.

![A placeholder image]({{<placeholder 600 300>}}){#fig-placeholder}

::: column-page
![A full width placeholder image]({{<placeholder 1200 300>}}){#fig-placeholder2}
:::

### Tables

Tables can be created using the `kable` function from the `knitr` package. See an example in @tbl-iris. Use the `column-page` class to make the table take the full page width (for wider tables).

See also [Quarto documentation](https://quarto.org/docs/authoring/tables.html).

```{r}
#| label: tbl-iris
#| echo: false
#| tab-cap: The first rows of the iris dataset.

knitr::kable(head(iris), caption = "The first rows of the iris dataset.")
```

{{< lipsum 3 >}}

## State of the Art

{{< lipsum 10 >}}

## Research Questions

{{< lipsum 3 >}}
